ChemKED: a human- and machine-readable data standard for chemical kinetics experiments

### 2017-02-21 pyked.tex
mostly spacing updates

The \ck{} file is a YAML-format file. This format offers the advantage of being
human readable, written in plain text, and having parsers in most common
programming languages, including Python, C++, Java, Perl, MATLAB, and many
others. The YAML syntax is quite simple. The basic file structure is made of
mappings, delimited by a colon. The key for the mapping is on the left of the
colon, and the value on the right can be a single value, a sequence of values, or a nested mapping:

\begin{minted}{yaml}
    key1: value  # Single-value mapping
    key2: [0, 1, 2]  # Mapping with sequence
    key3:  # Alternative sequence format
      - 0
      - 1
    key4:  # Nested mapping
      key5: 0
\end{minted}

The \yaml|value| can be a string, integer, or floating point number. The type is
inferred from the \yaml|key| when the value is read. The \ck{} format is
designed to include all of the information necessary to simulate a given
experiment. The \ck{} format can be broken into two main sections. The first
section details all of the ``meta'' information about the experiment and the
\ck{} file. In this section, the common \yaml|author| mapping is used for any
fields where an author must be specified. The \yaml|author| mapping contains the
following fields:
%
\begin{itemize}
    \item \yaml|name| (required, string): The author's full name
    \item \yaml|ORCID| (optional, string): the author's ORCID number
\end{itemize}
%
More generally for the meta information, the required keys in this section
are:
%
\begin{itemize}
    \item \yaml|file-author| (required, \yaml|author|-type mapping): The author
    of the \ck{} file
    \item \yaml|file-version| (required, integer): The version of the \ck{} file
    \item \yaml|chemked-version| (required, string): The version of the \ck{}
    schema that this file conforms to
    \item \yaml|reference| (required, mapping): The reference information for
    the article associated with the data in the file. The fields in this
    mapping are:
    \begin{itemize}
        \item \yaml|authors| (required, sequence): A sequence of \yaml|author| mappings
        \item \yaml|journal| (required, string): The name of the publishing journal
        \item \yaml|year| (required, integer): The year of publication
    \end{itemize}
    \item \yaml|experiment-type| (required, string): One of \yaml|ignition delay| or \yaml|flame speed|
    \item \yaml|apparatus| (required, string): The type of apparatus used to perform the experiment
\end{itemize}

>>>>

The \ck{} file is a YAML-format file. This format offers the advantages of being
human readable, written in plain text, and having parsers in most common
programming languages, including Python, C++, Java, Perl, MATLAB, and many
others. The YAML syntax is quite simple. The basic file structure is made of
mappings, delimited by a colon. The key for the mapping is on the left of the
colon, and the value on the right can be a single value, a sequence of values,
a nested mapping, or some combination of these:

\begin{minted}{yaml}
    key1: value  # Single-value mapping
    key2: [0, 1, 2]  # Mapping with sequence
    key3:  # Alternative sequence format
      - value
      - value
    key4:  # Nested mapping
      key5: 0
\end{minted}

The \yaml|value| can be a string, integer, or floating point number. The type is
inferred from the \yaml|key| when the value is read. The \ck{} format is
designed to include all of the information necessary to simulate a given
experiment and can be broken into two main sections. The first section details
all of the ``meta'' information about the experiment and the \ck{} file. In this
section, the common \yaml|author| mapping is used for any fields where an author
must be specified. The \yaml|author| mapping contains the following fields:
%
\begin{itemize}
    \item \yaml|name| (required, string): The author's full name
    \item \yaml|ORCID| (optional, string): the author's ORCID number
\end{itemize}
%
More generally for the meta information, the required keys in this section
are:
%
\begin{itemize}
    \item \yaml|file-author| (required, \yaml|author|-type mapping): The author
    of the \ck{} file
    \item \yaml|file-version| (required, integer): The version of the \ck{} file
    \item \yaml|chemked-version| (required, string): The version of the \ck{}
    schema that this file conforms to
    \item \yaml|reference| (required, mapping): The reference information for
    the article associated with the data in the file. The fields in this
    mapping are:
    \begin{itemize}
        \item \yaml|authors| (required, sequence): A sequence of \yaml|author|
        mappings
        \item \yaml|journal| (required, string): The name of the publishing
        journal
        \item \yaml|year| (required, integer): The year of publication
    \end{itemize}
    \item \yaml|experiment-type| (required, string): One of \yaml|ignition
    delay| or \yaml|flame speed|
    \item \yaml|apparatus| (required, string): The type of apparatus used to
    perform the experiment
\end{itemize}
